Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-06-27 main_revision.tex

\textbf{Growth respiration)}, \emph{`grperc'}, or the (fixed) fraction of carbon spent on respiration per unit of new tissue, was revised substantially in CLM5 to reflect new estimates that account for methodological issues with the observation of growth respiration (Atkin O., pers comm.) from 0.3 to 0.11. CLM5 further adopts a new leaf maintenance respiration scheme, based on \cite{atkin2015}, which significantly increases maintenance respiration costs. Here we test the impacts of this change on overall carbon budgets.

@@

\textbf{Leaf maintenance respiration intercept}, \emph{lmr\_intercept}. The new leaf maintenance respiration model, proposed by \cite{atkin2015} and adopted by CLM5, has it's intercept (but not slope) as a PFT dependant parameter, with variation between PFTs reported by \cite{atkin2015} and used herein. Here we test the impacts of the uncertainty in the observations of this parameter.

\textbf{Fraction of uptake that is ectomycorrhizal}, \emph{frac\_ecto}, is an ecosystem-level property defined by the FUN model which allows the proportions of the fungal symbiotic pathways to be modified. Default parameters are as provided by \cite{shi2016}.

\textbf{Parameters a,b and c of the flexible C:N model linked to FUN}, \emph{cn\_flex\_a, cn\_flex\_b, \& cn\_flex\_c}, as described in the CLM5 technical note, determine the response of tissue C:N ratios to depletion of N in both the environment and the plant tissues themselves.

\subsubsection{Parameter Ranges}
\emph{SLA} and \emph{leafcn} are readily observable and thus among the most common traits represented in the TRY plant trait database (\url{www.try-db.org}). We derive values from the analysis by (\cite{kattge2011}) for their mean and distribution. For both parameters, values are log-normally distributed. We here take the PFT average log-normalised standard deviation range from TRY and apply it across all PFTs (thus the lower bounds are closer to the mean than the higher bounds, Table \ref{table_ranges}). The range of \emph{fracfixers} and \emph{frac\_ecto} were set to vary across their whole logical range from 0 to 1 (0 to 100\% of ecosystem productivity being available for fixation or ectomycorrhizal uptake).  \emph{grperc} ranges from its logical lower bound of zero up to the range of the previously used CLM(4, 4.5) value (0.3). \emph{lmr\_intercept} and \emph{medlyn\_slope} are both set such that the range of values tested represents the range across all the PFTs reported in \cite{atkin2015} and \cite{dekauwe2015}. Reasonable ranges of the \emph{cn\_flex} parameters are unknown, since these physiological controls are poorly understood. Thus, we explore an order of magnitude in each direction from the default, to obtain an understanding of the general sensitivity to this parameterization (thus, these results should not be interpreted as covering a constrained range of variation). The same issues apply to $N_{costs}$ parameters.

\section{Results}
Our analysis used four sites, with thirteen parameters perturbed to four different values, each of those with control, CO$_{2}$ and N fertilization simulations. Including the default simulations, the total comprises 636 different run configurations. We examine the parametric responses of five output variables chosen for their importance in the overall biogeochemical system (GPP, NPP, LAI, leaf nitrogen  ($N_{area}$, gN m$^{-2}$), and total vegetation carbon (g m$^{-2}$). We did not look at soil output variables as our parameter analysis is focused on vegetation responses.

@@

The variance in \emph{lmr\_intercept} (across the range of reported intercepts in \cite{atkin2015}) also has important consequences for ecosystem productivity, broadly in line first-order expectations.  At Caxiuan\~a, the warmest site here, the \emph{lmr\_intercept} was one of the most important contributing factors to the NPP, LAI and vegetation carbon states. Whether the full range of values reported by \cite{atkin2015} is an appropriate reflection of the range of uncertainty for all PFTs is debatable, and a narrower range might be discernible with finer interpretation of their data.

\emph{frac\_ecto\_fungi}, the fraction of ectomycorhizzal vs arbuscular fungi had limited impact here, suggesting that the parameterization of the varying costs between these uptake pathways did not have a large impact on N uptake. This suggests that this difference is overridden by other parts of the dynamics parameterized in FUN.

\emph{cn\_flex\_a} is the intercept above which an increase in the cost of N will reduce expenditure on N uptake (see \href{https://escomp.github.io/ctsm-docs/doc/build/html/tech_note/FUN/CLM50_Tech_Note_FUN.html#modifications-to-allow-variation-in-c-n-ratios} for details). Thus, low values of \emph{cn\_flex\_a} result in reductions in expenditure on N uptake when N is too expensive, and therefore in lower tissue N content, and vice-versa.   For the range of parameters and the sites investigated here, this parameter had limited impact on the system state.  Increasing \emph{cn\_flex\_b} also increases the amount of carbon spent on N uptake when costs are high, and also has limited impacts on the system state here. \emph{cn\_flex\_c} affects the degree to which plants attempt to maintain tissue C:N values near to their target when environmental costs are varying. For the state impacts here, the role of this parameter was limited, but for the step-change fertilizations it was much more important, so we will discuss it's role further in the section below.

>>>>

@@

\textbf{C:N flexibility }, \emph{cn\_flex\_a, cn\_flex\_b, \& cn\_flex\_c},  as described in the CLM5 technical note, determine the response of tissue C:N ratios to depletion of N in both the environment and the plant tissues themselves. Only the thid parameter (c) had an important impact in this sensitivity analysis, and so we focus here on the impact of that parameter.

Other variables we tested in earlier versions of the analysis included rate constant controlling the growth and maintenance respiration rates, the fraction of ectomycorrhizal fungi, and parameters 'a' and 'b' of the flexible C:N ratio model. None of these had important impacts on the fertilization responses, and growth and respiration rates affected the model state in a linear and predictable fashion, thus they are omitted here but can be accessed via the available simulations.

\subsubsection{Parameter Ranges}
\emph{SLA} and \emph{leafcn} are readily observable and thus among the most common traits represented in the TRY plant trait database (\url{www.try-db.org}). We derive values from the analysis by (\cite{kattge2011}) for their mean and distribution. For both parameters, values are log-normally distributed. We here take the PFT average log-normalised standard deviation range from TRY and apply it across all PFTs (thus the lower bounds are closer to the mean than the higher bounds, Table \ref{table_ranges}). The range of \emph{fracfixers} and was set to vary from 0 to 100\% of ecosystem productivity being available for fixation.  \emph{medlyn\_slope} varies across the stndard errors reported in \cite{dekauwe2015}. Reasonable ranges of the \emph{cn\_flex} parameters are unknown, since these physiological controls are poorly understood. Thus, we explore an order of magnitude in each direction from the default, to obtain an understanding of the general sensitivity to this parameterization. The same issues apply to $N_{costs}$ parameters.

\section{Results}
Our analysis used four sites, with eight parameters perturbed to four different values, each of those with control, CO$_{2}$ and N fertilization simulations.  We examine the parametric responses of five output variables chosen for their importance in the overall biogeochemical system (GPP, NPP, LAI, leaf nitrogen  ($N_{area}$, gN m$^{-2}$), and total vegetation carbon (g m$^{-2}$). We did not look at soil output variables as our parameter analysis is focused on vegetation responses.

@@

 \emph{cn\_flex\_c} affects the degree to which plants attempt to maintain tissue C:N values near to their target when environmental costs are varying. For the state impacts here, the role of this parameter was limited, but for the step-change fertilizations it was much more important, so we will discuss it's role further in the section below.
